Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-08-19 research_class/paper.tex
paper.tex: add testing pgfplots graphs/plots.

@@

\section{Use Cases}
The traditional use of distributed consensus is in the data-center
(private or cloud based) especially as the core coordination component
of a replicated data-storage system. In these examples, the set of
nodes that compose the cluster tend to be fairly static and changes to
cluster membership are usually for the purpose of replacing nodes.
Changes to the long term size of the cluster are uncommon.

@@

\section{Outcome}

\subsection{Testing}

@@

\subsection{Results}

@@

@@

\begin{enumerate}
\item Explore the use of alternate WebRTC transport modes for relaxing
  ordering constraints and delivery guarantees. Since the Raft
  protocol is tolerant of out-of-order and dropped messages, it is
  possible that Raft over WebRTC could be more efficient with these
  one or both of these constraints relaxed.
\item Test the survivability of the cluster when the signaling server is
  becomes completely unresponsive or just very slow.
\item Implement a full online chat system with linearizable guarantees for
  the chat message ordering.
\item Explore models for dynamically adjusting Raft timeout values to
  account for changing network and browser conditions.
\item Test the ability of the system to catch up stale nodes by
  disconnecting one or more nodes, run the cluster for some period
  time with transactions created periodically, and then reconnect the stale
  clients.
\item Implement and test forwarding client requests rather than default
  redirecting the client to the leader. In other words, allow client
  requests to originate from any node of the cluster and be redirected
  automatically to the leader (rather than the current manual
  process).
\item Perform quantitative and real-world testing to better characterize
  the performance, availability and scalability characteristics of the
  system.
\item Implement a user interface for sending commands to the transaction
  log and for viewing the current state of the Raft state machine.
\item Explore models for dealing with the case where the cluster goes from
  two nodes down to one node. Can usefulness and availability be
  improved without sacrificing Raft safety constraints.
\item Test the system in more various network environments. Determine the
  reliability of establishing direct browser-to-browser communication.
  Determine if corporate firewalls make this as difficult as is
  implied in some of the documentation and standards texts.
\item Implement and test forwarding client requests rather than default
  redirecting the client to the leader. In other words, allow client
  requests to originate from any node of the cluster and be redirected
  automatically to the leader (rather than the current manual
  process).
\item Perform quantitative and real-world testing to better characterize
  the performance, availability and scalability characteristics of the
  system.
\item Implement a user interface for sending commands to the transaction
  log and for viewing the current state of the Raft state machine.
\item Explore models for dealing with the case where the cluster goes from
  two nodes down to one node. Can usefulness and availability be
  improved without sacrificing Raft safety constraints.
\item Test the system in more various network environments. Determine the
  reliability of establishing direct browser-to-browser communication.
  Determine if corporate firewalls make this as difficult as is
  implied in some of the documentation and standards texts.
\item Explore models for timing out and automatically removing nodes
  when they become unresponsive without needing to be notified by the
  signaling server that the nodes have disconnected.
\item Test larger scale deployments across multiple systems. Determine the
  factors that affect scalability and characterize scaling limits.
\item Perform wider cross-browser testing including Internet Explorer and
  Opera.
\item Implement Raft log compaction.
\item Explore models that allow for a combination of strict shared state
  and high performance bulk data such as media or object blobs. For
  example, the data with full consensus might contain hashes that to
  the refer to bulk data.
\item Implement a Node.js based Raft over WebRTC application. This would
  allow non-browser contexts to participate in the Raft cluster
  together with the browser clients. PeerJS issue
  [103](https://github.com/peers/peerjs/issues/103) must be resolved
  for this to be feasible.
\item Explore a design where some nodes of the cluster are non-voting and
  are not counted as part of transaction commit quorum. However, these
  nodes would still be included in the log replication algorithm. One
  model this would enable would be a configuration where a small group
  of voting nodes serve as the hub for a larger group of non-voting
  nodes. This may enable higher scaling of the system. It also enables
  interesting applications such as a logging or backup nodes.
\item Implement and test forwarding client requests rather than default
  redirecting the client to the leader. In other words, allow client
  requests to originate from any node of the cluster and be redirected
  automatically to the leader (rather than the current manual
  process).
\item Perform quantitative and real-world testing to better characterize
  the performance, availability and scalability characteristics of the
  system.
\item Implement a user interface for sending commands to the transaction
  log and for viewing the current state of the Raft state machine.
\item Explore models for dealing with the case where the cluster goes from
  two nodes down to one node. Can usefulness and availability be
  improved without sacrificing Raft safety constraints.
\item Test the system in more various network environments. Determine the
  reliability of establishing direct browser-to-browser communication.
  Determine if corporate firewalls make this as difficult as is
  implied in some of the documentation and standards texts.
\item Explore models for timing out and automatically removing nodes
  when they become unresponsive without needing to be notified by the
  signaling server that the nodes have disconnected.
\item Test larger scale deployments across multiple systems. Determine the
  factors that affect scalability and characterize scaling limits.
\item Perform wider cross-browser testing including Internet Explorer and
  Opera.
\item Implement Raft log compaction.
\item Explore models that allow for a combination of strict shared state
  and high performance bulk data such as media or object blobs. For
  example, the data with full consensus might contain hashes that to
  the refer to bulk data.
\item Implement a Node.js based Raft over WebRTC application. This would
  allow non-browser contexts to participate in the Raft cluster
  together with the browser clients. PeerJS issue
  [103](https://github.com/peers/peerjs/issues/103) must be resolved
  for this to be feasible.
\item Explore a design where some nodes of the cluster are non-voting and
  are not counted as part of transaction commit quorum. However, these
  nodes would still be included in the log replication algorithm. One
  model this would enable would be a configuration where a small group
  of voting nodes serve as the hub for a larger group of non-voting
  nodes. This may enable higher scaling of the system. It also enables
  interesting applications such as a logging or backup nodes.
\end{enumerate}

>>>>

\usepackage{pgfplots}
\pgfplotsset{compat=1.5}

@@

\section{Motivation/Use Cases}
The traditional use of distributed consensus is in the data-center
(private or cloud based) especially as the core coordination component
of a replicated data-storage system. In these examples, the set of
nodes that compose the cluster tend to be fairly static and changes to
cluster membership are usually for the purpose of replacing nodes.
Changes to the long term size of the cluster are uncommon.

@@

\section{Results}

\subsection{Manual Testing}

\subsubsection{Setup}

@@

\subsubsection{Outcome}

@@

\subsection{Automated Testing}

\subsubsection{Setup}

TBD: Setup for the automated tests.

Description of SlimerJS

Creation of SlimerJS test scripts using JavaScript.

\subsubsection{Outcome}

TBD: Outcome of the automated tests.

\begin{tikzpicture}
    \begin{axis}[
            title=Initial Cluster Activation,
            xlabel={Nodes},
            ylabel={Time (ms)},
            grid=major,
        ]
        \addplot table {data/data_cluster_up.dat};
    \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
    \begin{axis}[
            title=Message Propagation,
            xlabel={Nodes},
            ylabel={Time (ms)},
            grid=major,
        ]
        \addplot table {data/data_cluster_up.dat};
    \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
    \begin{axis}[
            title=Node Failure Recovery,
            xlabel={Nodes},
            ylabel={Time (ms)},
            grid=major,
            legend entries={$Leader Down$,$Half Cluster Down$},
        ]
        \addplot table {data/data_kill_leader.dat};
        \addplot table {data/data_kill_half.dat};
    \end{axis}
\end{tikzpicture}

@@

\begin{enumerate}
\item Explore the use of alternate WebRTC transport modes for relaxing
  ordering constraints and delivery guarantees. Since the Raft
  protocol is tolerant of out-of-order and dropped messages, it is
  possible that Raft over WebRTC could be more efficient with these
  one or both of these constraints relaxed.
\item Test the survivability of the cluster when the signaling server is
  becomes completely unresponsive or just very slow.
\item Explore models for dynamically adjusting Raft timeout values to
  account for changing network and browser conditions.
\item Test the ability of the system to catch up stale nodes by
  disconnecting one or more nodes, run the cluster for some period
  time with transactions created periodically, and then reconnect the stale
  clients.
\item Implement a user interface for sending commands to the transaction
  log and for viewing the current state of the Raft state machine.
\item Explore models for dealing with the case where the cluster goes from
  two nodes down to one node. Can usefulness and availability be
  improved without sacrificing Raft safety constraints.
\item Test the system in more various network environments. Determine the
  reliability of establishing direct browser-to-browser communication.
  Determine if corporate firewalls make this as difficult as is
  implied in some of the documentation and standards texts.
\item Implement and test forwarding client requests rather than default
  redirecting the client to the leader. In other words, allow client
  requests to originate from any node of the cluster and be redirected
  automatically to the leader (rather than the current manual
  process).
\item Perform quantitative and real-world testing to better characterize
  the performance, availability and scalability characteristics of the
  system.
\item Explore models for timing out and automatically removing nodes
  when they become unresponsive without needing to be notified by the
  signaling server that the nodes have disconnected.
\item Test larger scale deployments across multiple systems. Determine the
  factors that affect scalability and characterize scaling limits.
\item Perform wider cross-browser testing including Internet Explorer and
  Opera.
\item Implement Raft log compaction.
\item Explore models that allow for a combination of strict shared state
  and high performance bulk data such as media or object blobs. For
  example, the data with full consensus might contain hashes that to
  the refer to bulk data.
\item Implement a Node.js based Raft over WebRTC application. This would
  allow non-browser contexts to participate in the Raft cluster
  together with the browser clients. PeerJS issue
  [103](https://github.com/peers/peerjs/issues/103) must be resolved
  for this to be feasible.
\item Explore a design where some nodes of the cluster are non-voting and
  are not counted as part of transaction commit quorum. However, these
  nodes would still be included in the log replication algorithm. One
  model this would enable would be a configuration where a small group
  of voting nodes serve as the hub for a larger group of non-voting
  nodes. This may enable higher scaling of the system. It also enables
  interesting applications such as a logging or backup nodes.
\end{enumerate}
